A thesis draft

### 2018-11-30 res/sections/20-VNFImplementaton.tex
Fix English typos

As already cited, Harbor acts as a MANO, orchestrating and managing VNFs and the
related services. From the SFC point of view, it carries consistency checks when
a NS definition is created. The checks are carried out based on the VNF ID.
While the VNF definitions corresponds to a YAML Kubernetes configuration, the NS
one is a JSON array, for example:

@@

All the SFC-related components have been developed with the idea of being
containerized. This is a fundamental concept, because in this way all the
components have the possibility to run inside Kubernetes, granting them the
scalability and persistence benefits. On top of that, the use of
\verb!Deployment! granted the possibility to perform easy an update of already
existing components.

@@

Another important aspect to keep in consideration is how communications inside
the chain are performed. The packet arriving in the ingress needs to be
preserved, so that VNFs can perform packet elaboration. In order to obtain this,
packet encapsulation has been used. IP in IP encapsulation allow to preserve the
original packet, making the incoming packet the payload of a new one.

Ironhide, which was introduced in the previous chapter, plays a crucial role in
the establishment of a end-to-end connection between the client and the
receiver. Ironhide is able to fulfill the ingress and the egress role, and it
provides the necessary tools to add and remove the SFC headers that gets appended
and removed.

Finally, we were able to create bidirectional chains, resistant to faults and
degradation that satisfy the defined requirements.

>>>>

As already cited, Harbor acts as a MANO, orchestrating and managing VNFs and the
related services. From the SFC point of view, it carries consistency checks when
a NS definition is created. The checks are carried out based on the VNF ID.
While the VNF definition corresponds to a YAML Kubernetes configuration, the NS
one is a JSON array, as illustrated in this example:

@@

All the SFC-related components have been developed with the idea of being
containerized. This is a fundamental concept, because in this way all the
components have the possibility to run inside Kubernetes, granting them the
scalability and persistence benefits. On top of that, the use of the Kubernetes
\verb!Deployment! feature granted the possibility to easily perform updates of
already existing components.

@@

Another important aspect to keep in consideration is how communications inside
the chain are performed. The packet arriving in the ingress needs to be
preserved, so that VNFs can perform packet elaboration. In order to obtain this,
packet encapsulation has been used. IP in IP encapsulation allows to preserve
the original packet, making the incoming packet the payload of a new one.

Ironhide, which was introduced in the previous chapter, plays a crucial role in
the establishment of an end-to-end connection between the client and the
receiver. Ironhide is able to fulfill the ingress and the egress role, and it
provides the necessary tools to add and remove the SFC headers.

Finally, we were able to create bidirectional chains, resistant to faults and
degradations that satisfy the defined requirements.

### 2018-11-30 res/sections/25-TestsResponsiveness.tex
Fix English typos

\chapter{Tests and metrics}
\label{chap:test}
After the test-bed implementation, tests about its performance and metrics were
gathered in order to understand the real project effectiveness. We performed
tests relatively two main sections: one testing the architecture overall
responsiveness and one checking the SFC implementation and efficiency.

@@

Regarding the overall system responsiveness, a metric we considered worth to 
test was the VNF start up time in a docker environment versus one virtualized 
through a common virtual machine system (in this case Virtual Box was chosen). 
To make this simulation as fair as possible, we used the same node (an 
Openstack VM with 32GB of RAM, 8 vCPU and solid state storage) and used the 
same ``boot sequence'' for both the VNFs: first we launched the Astaire 
framework, ensuring its availability to process data and then we notified the 
test machine of the successful boot. The start-up time was measured from the 
beginning of the start-up command (\verb!docker run! for Docker and 
\verb!VBoxManage -s! for Virtual Box) till the first TCP hit received by the 
test back-end (to make things as smooth as possible, \verb!netcat! was used 
to listen to incoming TCP data).

@@

\noindent As is possible to see from the YAML definition, the test involved, for
every launch (that included and $N = 100$, for a total for 1000 tests), the 
download of the container image from the Docker hub repositories. This, while 
it forced every node to delete and download the image for each test, it ensured 
consistent measurements in cases where the selected node for the deployment did 
not have the image already pulled. In addition to that, another consideration 
needs to be taken into account: when the chain consists of two or more 
elements, the container image which is used for the container deployment is the 
same for every VNF involved, thus reducing the start up time for the subsequent 
pods that reside in nodes that have already deployed one.

@@

These additional operations implicate some time overhead, that cause the
deployment of a single Pod with a single container to be way longer that the
deployment of a simple container directly from Docker.

>>>>

\chapter{Tests and metrics}
\label{chap:test}
After the test-bed implementation, tests about its performance and metrics were
gathered in order to understand the real project effectiveness. We performed
tests relatively the architecture overall responsiveness.

@@

Regarding the overall system responsiveness, a metric we considered worth to
test was the VNF start up time in a docker environment versus one virtualized
through a common virtual machine system (in this case Virtual Box was chosen).
To make this simulation as fair as possible, we used the same node (an Openstack
VM with 32GB of RAM, 8 vCPU and solid state storage) and used the same ``boot
sequence'' for both the VNFs: first we launched the Astaire framework, ensuring
its availability to process data and then we notified the test machine of the
successful boot. The start-up time was measured from the beginning of the
start-up command (\verb!docker run! for Docker and \verb!VBoxManage -s! for
Virtual Box) till the first packet was received by the test back-end (to make
things as smooth as possible, \verb!netcat! was used to listen to incoming
data).

@@

\noindent As is possible to see from the YAML definition, the test involved, for
every launch (that included an $N = 100$, for a total for 1000 tests), the
download of the container image from the Docker hub repositories. This, while it
forced every node to delete and download the image for each test, it ensured
consistent measurements in cases where the selected nodes for the deployment did
not have the image already pulled. In addition to that, another consideration
needs to be taken into account: when the chain consists of two or more elements,
the container image which is used for the container deployment is the same for
every VNF involved, thus reducing the start up time for the subsequent pods that
reside in nodes that have already deployed one.

@@

These additional operations implicate some time overhead, that causes the
deployment of a single Pod with a single container to be way longer that the
deployment of a simple container directly from Docker.

### 2018-11-30 res/sections/79-Conclusions.tex
Fix English typos

Finally, we corroborated our implementation with tests and metrics, showing 
that a containerized approach is faster and more reliable and faster than a 
virtualized one, and illustrating that latency in communications through SFCs, 
while there is room for improvement, are decent considered that this is just 
a test-bed implementation.

@@

Generally speaking, I have never designed and though a software architecture of
these dimensions. The multiple attempts and issues I faced during the thesis
taught me more that I would have though, showing that, in life, you never end to
learn something new. Its for this reason that I think this project is something
more than a simple thesis, because I was put in front of challenges that seemed
over my possibilities at first, but that revealed to be no more than any other
common problem after having spent time analyzing, studying and understanding
them. At the end, I consider every second of my time spent on this thesis worth
it, and it gave me the confidence that every limit you face in life can be
broken down.

>>>>

Finally, we corroborated our implementation with tests and metrics, showing 
that a containerized approach is faster and more reliable and faster than a 
virtualized one.

@@

Generally speaking, I have never designed and thought a software architecture of
these dimensions. The multiple attempts and issues I faced during the thesis
taught me more that I would have though, showing that, in life, you never end to
learn something new. Its for this reason that I think this project is something
more than a simple thesis, because I was put in front of challenges that seemed
over my possibilities at first, but that revealed to be no more than any other
common problem after having spent time analyzing, studying and understanding
them. At the end, I consider every second of my time spent on this thesis worth
it, and it gave me the confidence that every limit you face in life can be
broken.
